Ensemble Stability of Biological Networks

### 2014-09-26 paper.tex
add figure showing symmetries of robustness

>>>>

As can be seen from \ref{eq:sccrobustness}, all that is required to fix robustenss is a set of SCC sizes and the number of links between them. This demonstrates that robustness is symmetric under the transformations shown in \ref{fig:hiertransformations}A and B. Since transformations of the type \ref{fig:hiertransformations}C change the number of links between connected components, this symmetry of $\hier$ is broken by \ref{eq:sccrobustness}. Nevertheless, a considerable degree of symmetry remains. For example, \ref{fig:robustnesssymmetries} shows the symmetry groupoid of robustness for the case in which we fix connected component sizes $\{2,1,1\}$ with a total of $3$ links between them.

### 2014-09-26 tex/figures.tex
add figure showing symmetries of robustness

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=1.0\columnwidth]{fig/combinedfigs.pdf}
\caption{{\bf Characterization of stability and robustness according to properties of system structure} (A) Stability versus connectivity, (B) robustness versus connectivity, (C) robustness versus number of cycles, (D) robustness versus graph edit distance%, (E) robustness versus number of cycles and connectivity, and (F) robustness versus graph edit distance and connectivity
 for three component systems.
}
\label{fig:combined}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/connectdist3D3x3.pdf}
\caption{{\bf Robustness versus graph edit distance and connectivity for three component systems.} }
\label{fig:connectdist3D3x3}
\end{figure}

>>>>

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=1.0\columnwidth]{fig/combinedfigs.pdf}
\caption{{\bf Characterization of stability and robustness according to properties of system structure} (A) Stability versus connectivity, (B) robustness versus connectivity, (C) robustness versus number of cycles, (D) robustness versus hierarchy%, (E) robustness versus number of cycles and connectivity, and (F) robustness versus graph edit distance and connectivity
 for three component systems.
}
\label{fig:combined}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/connectdist3D3x3.pdf}
\caption{{\bf Robustness versus hierarchy and connectivity for three component systems.} }
\label{fig:connectdist3D3x3}
\end{figure}

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.9\columnwidth]{fig/robustnesssymmetries.pdf}
\caption{{\bf Example symmetries of robustness.} In this example, the connected component sizes are fixed at $\{2,1,1\}$ with a total of $3$ links between them. Red arrows correspond to transformations like \ref{fig:hiertransformations}A where SCCs are swapped whereas purple arrows correspond to transformations like \ref{fig:hiertransformations}B where links are moved between nodes within a SCC.}
\label{fig:robustnesssymmetries}
\end{figure}

### 2014-09-26 tex/figuressupp.tex
move stable region figure to supplement
add figure showing symmetries of robustness

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.5\columnwidth]{fig/region2x2.pdf}
\caption{{\bf Stability conditions on coefficients of the characteristic polynomial for two component systems.} The regions correspond to all possible relationships between the invariants determined by the characteristic polynomial. Colors correspond to the regions given in the main text Green: $R_{2000}$, Red: $R_{1100}$, Yellow: $R_{0200}$, Magenta: $R_{0002}$, Blue: $R_{0020}$.}
\label{fig:region2x2}
\end{figure}

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.5\columnwidth]{fig/region3x3.pdf}
\caption{{\bf Stability conditions on coefficients of the characteristic polynomial for three component systems.} Colors correspond to the following regions Green: $R_{3000}$, Red: $R_{1200}$, Yellow: $R_{1002}$, Blue: $R_{1020}$. This is the plane $s_3=1$.}
\label{fig:region3x3}
\end{figure}

>>>>

%!TEX root = ../paper.tex
% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.7\columnwidth]{fig/region2and3.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for two and three component systems.} The regions correspond to all possible relationships between the invariants determined by the characteristic polynomial.}
% \label{fig:region2and3}
% \end{figure}

% \pagebreak

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.5\columnwidth]{fig/region2x2.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for two component systems.} The regions correspond to all possible relationships between the invariants determined by the characteristic polynomial. Colors correspond to the regions given in the main text Green: $R_{2000}$, Red: $R_{1100}$, Yellow: $R_{0200}$, Magenta: $R_{0002}$, Blue: $R_{0020}$.}
% \label{fig:region2x2}
% \end{figure}

% \pagebreak

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.5\columnwidth]{fig/region3x3.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for three component systems.} Colors correspond to the following regions Green: $R_{3000}$, Red: $R_{1200}$, Yellow: $R_{1002}$, Blue: $R_{1020}$. This is the plane $s_3=1$.}
% \label{fig:region3x3}
% \end{figure}
